---
title: "p8105_hw6_sl5009"
author: "Shengzhi Luo"
date: "03/12/2021"
output: github_document
---

```{r,setup,include=FALSE}
library(tidyverse)
library(viridis)
library(p8105.datasets)
library(modelr)

knitr::opts_chunk$set(
  echo = TRUE,
  warning = FALSE,
  fig.width = 8,
  fig.height = 6,
  out.width = "90%"
)

options(
  ggplot2.continuous.colour = "viridis",
  ggplot2.continuous.fill = "viridis"
)

scale_colour_discrete = scale_colour_viridis_d
scale_fill_discrete = scale_fill_viridis_d

theme_set(theme_minimal() + theme(legend.position = "bottom"))
```

# Problem 1

## Load and clean the data

```{r}
birthweight_df=
  read_csv("./birthweight.csv") %>% 
  mutate(
    babysex=case_when(
      babysex=="1" ~ "male",
      babysex=="2" ~ "female"
    ),
    frace=case_when(
      frace=="1" ~ "White",
      frace=="2" ~ "Black",
      frace=="3" ~ "Asian",
      frace=="4" ~ "Puerto Rican",
      frace=="8" ~ "Other",
      frace=="9" ~ "Unknown"
    ),
    malform=case_when(
      malform=="0" ~"absent",
      malform=="1" ~ "present"
    ),
    mrace=case_when(
      mrace=="1" ~ "White",
      mrace=="2" ~ "Black",
      mrace=="3" ~ "Asian",
      mrace=="4" ~ "Puerto Rican",
      mrace=="8" ~ "Other"
    ),
    babysex=fct_infreq(babysex)
  ) %>% 
  replace(is.na(.), 0) %>% 
  select(-pnumlbw,-pnumsga)

```

We make babysex, frace, malform and mrace as factors and drop pnumlbw and pnumsga column since they are all 0.

## Propose a regression model for birthweight.

```{r}
fit_0 = lm(bwt ~ ., data = birthweight_df)
summary(fit_0)
fit_1 = lm(bwt ~ delwt + menarche + fincome + mheight + momage + mrace + smoken + wtgain + parity, data = birthweight_df)
summary(fit_1)
fit_2 = lm(bwt ~ delwt + menarche + fincome + mheight + momage + mrace + smoken + wtgain, data = birthweight_df)
summary(fit_2)
```

We compare the full model with the plain model and then we drop the factor "parity".

## Make a plot

```{r}
birthweight_df %>% 
  modelr::add_residuals(fit_2) %>% 
  modelr::add_predictions(fit_2) %>% 
  ggplot(aes(x = pred, y = resid)) +geom_point()+ geom_smooth()
  labs(x = "fitted values", y = "residuals")
```


## Compare my model to two onthers.

```{r}
cv_df = 
  crossv_mc(birthweight_df, 100) %>% 
  mutate(train = map(train, as_tibble),
         test = map(test, as_tibble)) %>% 
  mutate(
    my_model = map(train, ~lm(bwt ~ delwt + menarche + mheight + momage + mrace + smoken + wtgain, data = .x)),
    comp_1 = map(train,~lm(bwt ~ blength + gaweeks,data = .x)),
    comp_2 = map(train,~lm(bwt ~ bhead + blength + babysex 
                              + bhead*blength + bhead*babysex + blength*babysex 
                              + bhead*blength*babysex, data = .x))
  ) %>% 
  mutate(
    rmse_my_model = map2_dbl(my_model, test ,~rmse(model = .x,data = .y)),
    rmse_comp_1 = map2_dbl(comp_1, test ,~rmse(model = .x,data = .y)),
    rmse_comp_2 = map2_dbl(comp_2, test ,~rmse(model = .x,data = .y))
  )
```

```{r}
cv_df %>% 
  select(starts_with("rmse")) %>% 
  pivot_longer(
    everything(),
    names_to = "model", 
    values_to = "rmse",
    names_prefix = "rmse_") %>% 
  mutate(model = fct_inorder(model)) %>% 
  ggplot(aes(x = model, y = rmse)) + geom_violin()
```


# Problem 2

## Download data

```{r}
weather_df = 
  rnoaa::meteo_pull_monitors(
    c("USW00094728"),
    var = c("PRCP", "TMIN", "TMAX"), 
    date_min = "2017-01-01",
    date_max = "2017-12-31") %>%
  mutate(
    name = recode(id, USW00094728 = "CentralPark_NY"),
    tmin = tmin / 10,
    tmax = tmax / 10) %>%
  select(name, id, everything())
```

## Produce estimates


```{r}
bootstrap = 
  weather_df %>% 
  modelr::bootstrap(n = 5000) %>% 
  mutate(
    models = map(strap, ~lm(tmax ~ tmin, data = .x)),
    r_square = map(models, broom::glance),
    log_estimate = map(models, broom::tidy)
  ) %>% 
  select(-strap, -models) %>% 
  unnest(r_square) %>% 
  select(.id, r.squared, log_estimate) %>% 
  unnest(log_estimate) %>% 
  select(-std.error, -statistic, -p.value) %>% 
  mutate(term = recode(term, `(Intercept)` = "b0", tmin = "b1")) %>% 
  pivot_wider(
    names_from = term,
    values_from = estimate
  ) %>% 
  mutate(log_value = log(b0*b1))  
```

## Plot the distribution
```{r}
bootstrap %>% 
  ggplot(aes(r.squared)) + 
  geom_density()
```

As we can see , the r.squared estimate are normally distibuted.



```{r}
bootstrap %>% 
  ggplot(aes(log_value)) + 
  geom_density()
```
The log_value are also normally distributed.

## Provide a 95% confidence interval

```{r}
bootstrap %>% 
  summarize(
    ci_lower = quantile(r.squared, 0.025), 
    ci_upper = quantile(r.squared, 0.975)) %>%
    knitr::kable(digits = 2)
bootstrap %>% 
  summarize(
    ci_lower = quantile(log_value, 0.025), 
    ci_upper = quantile(log_value, 0.975)) %>%
  knitr::kable(digits = 2)
```


